\Large \bf \sys: Library-Oriented Program Analysis

### 2020-05-26 paper/draft.tex
Massive edits

Dynamic program analysis is a long-standing technique for obtaining information about program execution.
We present a set of new dynamic analysis techniques that target modern dynamic languages such as Python, Lua, and JavaScript, enabled by the fact that modern dynamic languages feature a module-import mechanism that loads code at runtime as a string.
These techniques use lightweight load-time code transformations that operate on the string representation of the module,
as well as the context to which it is about to be bound, to insert developer-provided, analysis-specific code into the module before it is loaded.
This code implements the dynamic analysis, enabling these techniques to capture all interactions around the library in unmodified production language runtime environments.
We implement these techniques in \sys, a system targeting the JavaScript ecosystem. 
Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.

@@

\section{Implementation of Dialysis for SSJ}
\label{impl}

@@

\sys's  development achieves goals \textbf{G1--3}~\sx{goals}, demonstrating that it is indeed feasible to build a framework that 
  operates as a library around an existing runtime,
  does not require learning a new language, and 
  gets meaningful information while operating only at library boundaries.
% Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
In this section, we report on \sys's performance characteristics:
% At a high level, we are interested in three questions:
  (i) the overheads of its underlying building blocks;
  (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
  (iii) \sys's behavior on realistic  multi-library applications.
% For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
% For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
% For the third question, we use a combination of real applications~\sx{macro}.

Several takeaways are worth highlighting.
Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.
\sys's library-level analysis adds a small overhead, less than $2\times$ for the vast majority of libraries and often less than $5ms$.
Finally, \sys scales to large applications with hundreds of libraries while interposing on several thousands of objects.

Experiments were conducted on a moderate server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
In terms of software, we used Docker version 18.09.7 running a minimal Ubuntu 14.04.6, Jalangi v2, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
All times reported are in \textbf{ms}, averaged over 1K runs;
  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type invariant discovery.

\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
% Each dependency can perform one of three operations, depending on its current state:
%   (i) invoke a call to a module it imports,
%   (ii) busy-wait for a specific amount of time, or
%   (iii) respond to calls by returning a value.
A second goal was to understand \sys's internal overheads in a controlled environment.
% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{\sys-augmented single-library programs}.
    The table shows the overheads of applying the three analyses to the test suites of eight libraries. % (with Minimist involving five test cases).
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
\toprule
                               & Base   &  SA   & PD     &   TID   \\
\midrule
Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
Minimist~\cite{minimist}       &        &       &        &         \\
~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
~~~-t2                         & 29.35  & 56.30 &  53.98 &  53.17  \\
~~~-t3                         & 30.34  & 59.13 &  55.76 &  55.34  \\
~~~-t4                         & 30.04  & 56.40 &  53.68 &  53.27  \\
~~~-t5                         & 30.24  & 58.17 &  55.07 &  54.76  \\
Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
yargs~\cite{yargs}             & 14.59  & 15.68 &  15.49 &  15.54  \\
chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
\bottomrule
\end{tabular*}
\label{tab:meso}
\vspace{-5mm}
\end{table}

@@

\begin{figure*}[t]
  \centering
   \includegraphics[width=0.95\textwidth]{./figs/meso.pdf}
  \caption{
    \textbf{Analysis overheads.}
    The plot compares single-library programs taken from Jalangi2 between three setups:
		(i) Vanilla JavaScript, (ii) global-use analysis with Jalangi2, (iii) global-use analysis with \sys.
    Global-use analysis is a simple analysis that tracks accesses of global variables in the program~\cf{meso}.
  }
  \label{fig:meso}
  \vspace{-3mm}
\end{figure*}

@@

In the first experiment, we collected a diverse set of eight popular libraries from npm, 
% used by thousands of other projects,
on the order of hundreds of lines of code.
As a workload, we used each library's internal test suite (one library, \ttt{minimist}, includes several test harnesses).
These tests stress functionality as expected by the library's authors and confirm that \sys does not break it.
We applied our three analyses, and compare their performance with the baseline (Tab.~\ref{tab:meso}).
The results show that executions augmented with analyses are within 2--3$\times$, averaging a 80\% slowdown for the largest libraries.
Different benchmarks put a different pressure on \sys's wrappers, which range between 23--257. % (shown by the analysis output).

In the second experiment, we apply \sys on Jalangi2's extensive test suite (Fig.~\ref{fig:meso}) and compare \sys's performance to that of Jalangi2.
We note that Jalangi2 improves significantly over Jalangi's performance~\cite{jalangi}, as it eschews record/replay capabilities.
To be fair in our performance comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

@@

Applying \sys to these applications generates analysis results that are 9--132$\times$ larger than the ones for single libraries.
However, the performance of analyzed code is on average still within 2--3$\times$ over the baseline performance.
The size of the resulting JSON files raises the challenge of analysis interpretability---surprisingly, just running Terminalizer with \ttt{--help} still returns more than 6K fragments from several libraries.
Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-name, not module identifier.
This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries.
% For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
We also squash cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but results in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{three}).
Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.

>>>>

Dynamic program analysis is a long-standing technique for obtaining information about program execution.
We present a new dynamic analysis approach that targets modern dynamic languages such as Python, Lua, and JavaScript, enabled by the fact that they feature a module-import mechanism that loads code at runtime as a string.
This approach uses lightweight load-time code transformations that operate on the string representation of the module, as well as the context to which it is about to be bound, to insert developer-provided, analysis-specific code into the module before it is loaded.
This code implements the dynamic analysis, enabling this approach to capture all interactions around the library in unmodified production language runtime environments.
We implement this approach in \sys, a system targeting the JavaScript ecosystem. 
Results show that \sys delivers up to an order of magnitude performance improvements over current state-of-the-art dynamic analysis systems, compatibility with over 50 libraries and applications, and support for a range of dynamic analyses, each implemented in under 100 lines of code.

@@

\section{Implementation: Server-Side JavaScript}
\label{impl}

@@

At a high level, we are interested in three main questions:

\begin{itemize}
  \item \textbf{Q1} Given its coarse granularity, is \sys useful?
    We answer this question in \S\ref{bg}, which shows three case-study multi-module analyses with practical implications.
    \sys operates at the right level of abstraction for answering important questions raised by today's software engineering practices.

  \item \textbf{Q2} Is it usable?
     We answer this question in \S\ref{impl}, by implementing these and other analyses.
    \sys operates as a library around a unmodified runtime environments, does not require investment in a new language, and leads to analysis expressions that are comparable to conventional frameworks.
    % Analyses expressed in \sys are about 4$\times$ smaller than equivalent analyses written for a heavy-weight instrumentation framework.

  \item \textbf{Q3} How does it perform? We answer this question here.
  For the most libraries, \sys overheads are under 5\%~\sx{meso}.
  \sys is about $22\times$ \todo{faster} than Jalangi, a state-of-the-art dynamic analysis framework~\sx{meso}.
  By executing on unmodified runtimes, \sys has significantly better compatibility:
    to execute, Jalangi requires significant library modifications~\sx{meso}.
  \sys scales to three large applications with hundreds of libraries while interposing on several thousands of objects~\sx{macro}.
  Most of the overheads come from tracking global variables, but loading-time wrapping and runtime interposition overheads are negligible~\sx{micro}
  % The majority of the overheads come from the use of \ttt{with}, a

% \sys's  development achieves goals \textbf{G1--3}~\sx{goals}, demonstrating that it is indeed feasible to build a framework that 
%   operates as a library around an existing runtime,
%   does not require learning a new language, and 
%   gets meaningful information while operating only at library boundaries.
% % Despite the fact that it operates at coarser granularity, as shown earlier~\sx{impl} \sys can express analyses that generate results useful in several practical scenarios.
% In this section, we report on \sys's performance characteristics:
% % At a high level, we are interested in three questions:
%   (i) the overheads of its underlying building blocks;
%   (ii) dialysis on real libraries, and how they compare to a production-grade dynamic analysis; and
%   (iii) \sys's behavior on realistic  multi-library applications.
% % For the first question, we use  synthetic micro-benchmarks that built to stress key elements of the system and confirm it works correctly~\sx{micro}.
% % For the second question, we use real libraries and compare them with an analysis written in Jalangi~\sx{meso}.
% % For the third question, we use a combination of real applications~\sx{macro}.

Experiments were conducted on a modest server with 4GB of memory and 2 Intel Core2 Duo E8600 CPUs clocked at 3.33GHz.
In terms of software, we used Docker version 18.09.7 running a minimal Ubuntu 14.04.6, Jalangi v2, Node.js v8.9.4 (bundled with V8 v6.1.534.50, LibUV v1.15.0, and npm v6.4.1), all atop a Debian Linux with kernel v4.4.0-134.
All times reported are in \textbf{ms}, averaged over 1K runs;
  \textbf{SA}, \textbf{PD}, and \textbf{TID} respectively stand for security analysis, performance diagnosis, and type invariant discovery.

% \begin{table}[t]
% \center
% \footnotesize
% \setlength\tabcolsep{3pt}
% \caption{
%   \footnotesize{
%     \textbf{Analysis results for the largest libraries.}.
%     The table shows the overheads of applying the three analyses to the test suites of eight libraries. % (with Minimist involving five test cases).
%   }
% }
% \begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll l}
% \toprule
%                                & Base   &  SA   & PD     &   TID   \\
% \midrule
% Classnames~\cite{classnames}   &  2.72  & 6.62  &  6.61  &  6.10   \\
% Debug~\cite{debug}             & 31.39  & 33.54 &  33.94 &  33.96  \\
% Minimist~\cite{minimist}       &        &       &        &         \\
% ~~~-t1                         & 31.46  & 60.13 &  60.00 &  56.62  \\
% ~~~-t2                         & 29.35  & 56.30 &  53.98 &  53.17  \\
% ~~~-t3                         & 30.34  & 59.13 &  55.76 &  55.34  \\
% ~~~-t4                         & 30.04  & 56.40 &  53.68 &  53.27  \\
% ~~~-t5                         & 30.24  & 58.17 &  55.07 &  54.76  \\
% Moment~\cite{moment}           & 31.73  & 48.04 &  49.23 &  44.95  \\
% yargs~\cite{yargs}             & 14.59  & 15.68 &  15.49 &  15.54  \\
% chalk~\cite{chalk}             & 17.37  & 24.42 &  26.01 &  26.32  \\
% colorette~\cite{colorette}     & 08.10  & 13.85 &  13.41 &  13.16  \\
% mkdirp~\cite{mkdirp}           & 116.37 & 1959.52 & 1392.64 & 1252 \\
% \bottomrule
% \end{tabular*}
% \label{tab:meso}
% \vspace{-5mm}
% \end{table}

@@

\begin{figure*}[t]
  \centering
   \includegraphics[width=\textwidth]{./figs/micro-packages.pdf}
  \caption{
    \textbf{Analysis performance overhead.}
    The plot shows the performance overhead of the three analyses for 45 libraries~\cf{meso}.
  }
  \label{fig:micro-packages}
  \vspace{-3mm}
\end{figure*}

@@

\heading{\sys on Popular Libraries}
For the first experiment, we perform a large-scale evaluation on 50 JavaScript packages from the npm ecosystem.
These libraries are highly popular, averaging \todo{xx-xx} weekly downloads (total: \todo{X}) and are depended upon by about \todo{XX} other packages or applications on average (total: \todo{X}).
These libraries are relatively small---adhering to known language trends~\cite{npmstudy:19}---simplifying compatibility inspection.

Each library was run against the test suite provided by its nominal developers, via \ttt{npm test}.
As these libraries are quite popular, they have received significant investment in their testing infrastructure, resulting into two main benefits for \sys's evaluation:
  (i) different tests stress different parts of the library and corresponding analysis primitives;
  (ii) even if most applications that import these libraries use only a fraction of their functionality, tests still cover the majority of provided functionality---\eg we observed test suites that were $10\times$ the size of the corresponding library.

Fig.~\ref{fig:micro-packages} shows the performance overhead of applying \sys on these libraries.
Overheads report on running each library's entire test suite under the three analyses and comparing against the non-\sys version.
On average, \sys's analyses add about 3.3ms per library causing 1.93\% slowdown;
  relative overheads between analyses are negligible (avg: $<$0.1ms).
For the largest of these libraries, we perform a lighter global-access analysis (not shown in Fig.~\ref{fig:micro-packages}).
This is slightly faster, adding a 3.2ms causing a 1.62\% slowdown.
We zoom into the sources of these overheads later~\sx{micro}.

\heading{\sys vs. Jalangi}
For the second experiment, we compare the performance of \sys to that of Jalangi.
Jalangi is a popular dynamic analysis framework for JavaScript;
  it provides fine-grained instrumentation by executing the program using a custom interpreter.
We note our use of Jalangi's v2.2.5 version:
  the v2 branch improves significantly over the performance of the original framework~\cite{jalangi}, as it eschews record/replay capabilities.

In terms of programs, we use Jalangi's extensive test suite.
This is not entirely by choice:
  Jalangi's interaction with the bare-bones libraries was hitting important parsing issues, and was further complicated by \ttt{npm test} (which is an external program outside Node, but tightly coupled with it).
It is important

(Fig.~\ref{fig:meso}).
We compare with and compare \sys's performance to that of Jalangi2.
To be fair in our performance comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

\begin{figure*}[t]
  \centering
   \includegraphics[width=\textwidth]{./figs/meso.pdf}
  \caption{
    \textbf{\sys vs. Jalangi.}
    The plot compares single-library programs taken from Jalangi between three setups:
		(i) Vanilla JavaScript, (ii) global-use analysis with Jalangi, (iii) global-use analysis with \sys.
    Global-use analysis is a simple analysis that tracks accesses of global variables in the program~\cf{meso}.
  }
  \label{fig:meso}
  \vspace{-3mm}
\end{figure*}

@@

Applying \sys to these applications generates analysis results that are 9--132$\times$ larger than the ones for single libraries.
However, the performance of analyzed code is on average still within 2--3$\times$ over the baseline performance.
The size of the resulting JSON files raises the challenge of analysis interpretability---just by running Terminalizer with \ttt{--help} returns more than 6K fragments from several (hundreds of) libraries.
Our routines for post-processing \sys's results compress by module name---\ie squashing duplicate reports by human-readable name, not file-system module identifier.
This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different libraries.
% For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
We also squash cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but results in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{three}).
Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.

\todo{Two types: zooming into prior benchmarks, and targeted micro packages}
\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
% Each dependency can perform one of three operations, depending on its current state:
%   (i) invoke a call to a module it imports,
%   (ii) busy-wait for a specific amount of time, or
%   (iii) respond to calls by returning a value.
A second goal was to understand \sys's internal overheads in a controlled environment.
% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.

\heading{Sources of Overbred}
To understand the sources of these overheads, we perform a series of micro-benchmarks with tight loops calling several ES-internal libraries without any I/O.
The primary source of overhead seems to be the use of JavaScript's \ttt{with} construct~\sx{}, 
The \ttt{with} construct dominates overheads, as it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards~\cite{}.
% Proxy objects exhibit a much lower cost.
% \TODO{Add some numbers from \ttt{t19} for different configs}.

\begin{figure}
  \centering
  \includegraphics[width=0.05\textwidth]{./figs/lya_donut_index}
  \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_obj}
  \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_unique_valid}
  \includegraphics[width=0.20\textwidth]{./figs/lya_ctx_total_valid}

  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_unique_invalid}
  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_total_invalid}
  \caption{
    \textbf{Access characteristics.}
    \todo{Explain}
  }
  \label{fig:objects}
\end{figure}

\begin{figure}[b!]
  \centering
  \includegraphics[width=\columnwidth]{./figs/lya_n_obj}
  \includegraphics[width=\columnwidth]{./figs/lya_unique_valid}
  % \includegraphics[width=\columnwidth]{./figs/lya_unique_invalid}
  \includegraphics[width=\columnwidth]{./figs/lya_total_valid}
  % \includegraphics[width=\columnwidth]{./figs/lya_total_invalid}
  \caption{
    \textbf{Depth vs. permissiveness.}
    From the top:
    (a) number of \sys wrappers,
    (b) unique valid accesses,
    (c) unique invalid accesses,
    (d) total valid accesses, and
    (e) total invalid accesses---all as a function of \todo{enforcement} depth.
  }
  \label{fig:objects}
\end{figure}
